---
title: "EcoSyst - Typification og generalised species datasets"
Author: Thijs Christiaan van Son and Olav Skarpaas
output: 
  html_notebook: 
    toc: yes
---

## Background
The code documents and illustrates the steps from data to type division
along a local environmental complex variable (LEC).


### Packages and source files
```{r, message=FALSE}
library(raster)
# library(fields)
library(vegan)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tibble)


source("../R/typification_functions.r")
```


### Simulating species
Could be worth checking out the "Virtual species" package for simulation of species.
For the current method, it seems the area under the curve always sums to one ...
Set a random seed?
```{r}
# Generating simulate species
sim_species <- sim_sp()

# Need to prepare data for plotting with ggplot
sim_species_lf <- as.data.frame(sim_species$sp_abun) %>% 
  gather(key = "species", value = "dens") %>% 
  add_column(lce = rep(1:100, 10))

# Plotting to show simulated species densities
pl <- ggplot(sim_species_lf, aes(x = lce, y = dens)) +
  geom_line(aes(colour = species)) +
  coord_cartesian(ylim = c(0, 1.4*max(sim_species_lf$dens))) +
  theme(legend.position = "none",
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  labs(x = "Key source of variation (local complex-variable)",
       y = "Key characteristic") 
pl
```


### Typification procedure

#### Hypothetical observations
Working with the simulated species abundance along a single LCE. 
Our hypothesis is that there are X types distributed evenly along the LCE.
```{r}
num_obs <- 15

# Hypothesis: Observation points of X candidate types, evenly distributed along the LCE
obs_pts <- round((1:num_obs) * 100 / (num_obs + 1), 0)


# Plotting
for (i in 1:num_obs) {
  text(obs_pts[i], 1.4*max(sim_species$sp_abun), i,
       add = TRUE)
}
```

